---
title: Evaluation of Embedding over Differnt Dimensions
output: 
  pdf_document:
    toc: true
    toc_depth: 3
    df_print: kable
---


```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

\newpage

## Description

For each dimension value, the process of embedding generation & evaluation will take about **26** to **30** mins depending on value size.
<br/>  
<br/>  

**Summary Data File:** `r summary_file`.

**Dimension Setting:** `r paste(dims, collapse = ", ")`.

**Co-occurrence File:** `r CO_file`.

**Multi-axial File:** `r HAM_file`.

**All Relation Pairs File:** `r ARP_file`.

**Evaluation Metric:** `r plot_val`.
<br/>  
<br/>  


```{r, echo=FALSE}
  
# get plot data
df_plot <- get_plot_data(summary, col = plot_val, labels = labels)  

# split data by group (Similarity, Relation, Others)
data_split <-  split_data(df_plot, patterns = split_patterns)

# reshape split data for plot
data_reshape <- lapply(names(data_split), function(x) {
  reshape_data(data_split[[x]], y = plot_val)
})
names(data_reshape) <- names(data_split)

```

## Evaluation Results {.tabset}

### Similarity
```{r, echo=FALSE}
if (is.null(data_reshape$Similarity)) {
  cat("Not contents.")
} else data_reshape$Similarity %>% plt(y = plot_val, method = "ggplot")
```


### Relation
```{r, echo=FALSE}
if (is.null(data_reshape$Relation)) {
  cat("Not contents.")
} else data_reshape$Relation %>% plt(y = plot_val, method = "ggplot")
```

      
### Other
```{r, echo=FALSE}
if (is.null(data_reshape$Other)) {
  cat("Not contents.")
} else data_reshape$Other %>% plt(y = plot_val, method = "ggplot")
```


### Data
```{r, echo=FALSE}
df_plot
```

