---
title: Evaluation of Embedding over Differnt Dimensions
output: html_document
---


```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## Description

For each dimension value, the process of embedding generation & evaluation will take about **26** to **30** mins depending on value size.<br/><br/>

**Summary Data File:** `r summary_file`.<br/>
**Dimension Setting:** `r paste(dims, collapse = ", ")`.<br/>
**Co-occurrence File:** `r CO_file`.<br/>
**Multi-axial File:** `r HAM_file`.<br/>
**All Relation Pairs File:** `r ARP_file`.<br/>
**Evaluation Metric:** `r plot_val`.<br/><br/>


```{r, echo=FALSE}
  
# get plot data
df_plot <- get_plot_data(summary, col = plot_val, labels = labels)

# split data by group (Similarity, Relation, Others)
data_split <-  split_data(df_plot, patterns = split_patterns)

# reshape split data for plot
data_reshape <- lapply(names(data_split), function(x) {
  reshape_data(data_split[[x]], y = plot_val)
})
names(data_reshape) <- names(data_split)

```

## Evaluation Results {.tabset}

### Similarity
```{r, echo=FALSE}
if (is.null(data_reshape$Similarity)) {
  cat("Not contents.")
} else data_reshape$Similarity %>% plt(y = plot_val, method = "plotly")
```
<br/><br/><br/>

### Relation
```{r, echo=FALSE}
if (is.null(data_reshape$Relation)) {
  cat("Not contents.")
} else data_reshape$Relation %>% plt(y = plot_val, method = "plotly")
```
<br/><br/><br/>
      
### Other
```{r, echo=FALSE}
if (is.null(data_reshape$Other)) {
  cat("Not contents.")
} else data_reshape$Other %>% plt(y = plot_val, method = "plotly")
```
<br/><br/><br/>

### Data
```{r, echo=FALSE}
DT::datatable(df_plot, options = list(scrollX = TRUE, scrollY = TRUE))
```
<br/><br/><br/>
