---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

# keser-i2b2

This is a package to:
- Generate Embedding
- Evaluate Embedding
- Get Evaluation Plots

## Installation

You can install the development version from GitHub with:

``` r
install.packages("remotes")
remotes::install_github("celehs/KESER-i2b2")
```

If you can't install it, alternative opntion is to download the repo and use `devtools::load_all()` to load the package. 

``` r
install.packages("devtools")
setwd("D:\\Projects\\harvard\\keser-i2b2")     # Set to your path
devtools::load_all()    
```

## Usage

Make sure you have the following files available:
- Hierarchy file, such as `MultiAxialHierarchy.csv`
- Relation pairs file, such as `AllRelationPairsWithNull.Rdata`
- Input data file, such as `rpdr_code_cooccurrence_victor_2019.csv`

Then, You can tune the dimensions on varaible `dims`, each dimension may take 26-30 mins to run. 

### Set up Parameters

For the file paths, change it base on your file locations.

```{r eval=FALSE}
library(keser-i2b2)
CO_file <- "dungeon//data//rpdr_code_cooccurrence_victor_2019.csv"  # Co-occurrence File: .csv/.parquet/.Rdata
HAM_file <- "dungeon//data//MultiAxialHierarchy.csv"                # Multi-axial Hierarchy File: .csv/.parquet/.Rdata  
ARP_file <- "dungeon//data//AllRelationPairsWithNull.Rdata"         # All Relation Pairs File: .csv/.parquet/.Rdata  
dims <- seq(200, 1000, 200)                                         # Dimension Setting
out_dir <- NULL                                                     # Output folder setting -  If NULL All Outputs Will Be At: working_dir/output
data_type <- 1                                                      # Input Data Type Setting, Codi Only:1, Codi & CUI: 2 
```


### Generate Embedding & Evaluation

```{r eval=FALSE}
summary <- get_eval_embed(CO_file, HAM_file, ARP_file, dims, out_dir)
```

The output of `get_eval_embed` is a list includes meta-data, embedding & evaluation results. The list will also be saved as `.Rdata`.

#### Generate Plot Report

```{r eval=FALSE}
get_report(summary, plot_val = "auc", knit_format = "html")
```

`get_report` will not return anything but creates the plot report under `out_dir` folder. If `out_dir` is ``NULL`` then it will create a folder called **output** in your working directly.

#### Check Results

The evaluation plots are saved as "Summary-XX-YY-ZZ.html", and the original summary data are saved as "Summary-XX-YY-ZZ.Rdata", where XX stands for starting dimension, YY stands for ending dimension and ZZ stands for Step. 

You can choose a proper dimension and use the corresponding embedding for the next steps.

